OptiFit: a fast method for fitting amplicon sequences to existing OTUs

### 2021-08-24 paper/paper.Rmd
Write figure caption for algorithm diagram
Finish importance section

<!--
- Go back through https://peerj.com/articles/1487/ to get all the arguments for why the qiime based methods are problematic…
1. The threshold with closed reference is a radius and with de novo its a diameter
2. The gg reference was defined for full length sequences, within a subregion there are duplicate and nearly duplicate sequences
3. Because VSEARCH/USEARCH is a greedy heuristic, its looking for a reference that is close. Although the ordering of the database is not relevant (it was with USEARCH) it gets the wrong number of its (see Figure 5)
-->

@@

**TODO.**
Advancements in DNA sequencing technology have allowed researchers to affordably
generate millions of reads from microorganisms in diverse natural communities.
allowing us to characterize communities.
\newpage

@@

KLS received support from the NIH Training Program in Bioinformatics (T32 GM070449).
Salary support for PDS came from NIH grants R01CA215574 and U01AI124255.

The funders had no role in study design, data collection and interpretation, 
or the decision to submit the work for publication.

>>>>

<!-- TODO
- Go back through https://peerj.com/articles/1487/ to get all the arguments for why the qiime based methods are problematic…
1. The threshold with closed reference is a radius and with de novo its a diameter
2. The gg reference was defined for full length sequences, within a subregion there are duplicate and nearly duplicate sequences
3. Because VSEARCH/USEARCH is a greedy heuristic, its looking for a reference that is close. Although the ordering of the database is not relevant (it was with USEARCH) it gets the wrong number of its (see Figure 5)
-->

@@

Advancements in DNA sequencing technology have allowed researchers to affordably
generate millions of reads from microorganisms in diverse natural communities.
Efficient software tools are needed to assign microbial sequences into
taxonomic groups for characterization and comparison of communities.
The OptiClust algorithm produces high quality groups by comparing sequences to
each other, but the taxonomic assignments can change when new sequences are
added to a dataset, making it difficult to compare different studies.
Other approaches assign sequences to taxonomic groups by comparing them to
sequences in a reference database to produce consistent assignments, but the
quality of the groups produced is reduced compared to OptiClust.
We developed OptiFit, a new reference-based algorithm that produces consistent
yet high quality taxonomic assignments like OptiClust.
OptiFit allows researchers to compare microbial communities across different
studies or add new data to existing studies without sacrificing the quality of
the taxonomic assignments.

\newpage

@@

We thank members of the Schloss Lab for their feedback on the figures.

KLS received support from the NIH Training Program in Bioinformatics (T32 GM070449).
Salary support for PDS came from NIH grants R01CA215574 and U01AI124255.
The funders had no role in study design, data collection and interpretation, 
or the decision to submit the work for publication.
